---
title: "Sensitive_privacy"
author: "Yixi Li"
date: "5/4/2019"
output: html_document
---
```{r data, include=FALSE}
library(lme4)
#library(MASS)
#library(MCMCglmm)
#install.packages("ordinal")
library(ordinal)
#library(R2MLwiN)

dir<-'/Users/Loielaine/Desktop/Good_Good_Study/2018Survey project/data/'

data<-read.csv2(paste0(dir,"interviewee_interviewer_complete.csv"))

#demo_r
age<-as.numeric(as.character(data$age))
#age<-scale(age,scale = F)
gender<-data$gender_n
data$ismarry<-0
data[data$marital==2,"ismarry"]<-1
marital<-data$ismarry
edu<-data$educ_nc
#nfamily<-data$nfamilya
nfamily<-data$nfamily_c
employ<-data$employment
muni<-data$muni_c

#demo_iwer
language_iw<-data$language_iw
nationality<-data$nationality_iw
#age_iw<-as.numeric(as.character(data$age_iw))
#age_iw<-scale(age_iw,scale = F)
edu_iw<-data$edu_iw
age_iw<-data$age_iwc
exp_iw<-data$experience_iw_cate
iw7a<-data$iw7a_cate
iw7b<-data$iw7b_cate
iw7b3<-data$iw7b_cate3
#iw9a<-data$iw9a_cate
iw9b<-data$iw9b_cate

#personality
#hexcao
hexcao<-data.frame(matrix(nrow=1502,ncol=6))
hexcao[,1]<-data$humility
hexcao[,2]<-data$emotionality
hexcao[,3]<-data$extraversion
hexcao[,4]<-data$agreeableness
hexcao[,5]<-data$conscientiousness
hexcao[,6]<-data$openess  
hexcao<-apply(hexcao,2,as.numeric) 
hexcao<-scale(hexcao,scale=F)

#SSI
ssi<-data.frame(matrix(nrow=1502,ncol=6))
ssi<-data[,627:632]
ssi<-apply(ssi,2,as.numeric)
ssi<-scale(ssi,scale=F)

#iwid
iwid<-as.character(data$iweraccount)

#weights
weights<-as.numeric(as.character(data$wgt))/sum(as.numeric(as.character(data$wgt)))*1502
#weights<-scale(weights,center = F)

strata<-data$strat

#bidr
bidr<-data$sum_orginal
summary(factor(bidr))

#family
family_var<-c("friend_diff","no_companion","traditions","rltp_partents_categorical",
                         "rltp_spouse_categorical","rltp_siblings_categorical",  "secret_spouse_categorical","secret_parent_categorical",
                         "hh_hit_categorical","hh_insult","event_mixed")
family_c<-data[,family_var]

#present
parent<-data$io1_parent
spouse<-data$io1_spouse
siblings<-data$io1_siblings
children<-data$io1_children
parentinlaw<-data$io1_parentinlaw
present<-data$present

modeldata<-data.frame(cbind(present,parent,spouse,siblings,children,parentinlaw,family_c,age,gender,edu,nfamily,employ,muni,marital,bidr,language_iw,nationality,age_iw,edu_iw,exp_iw,iw7b,iw7b3,iw9b,
hexcao,ssi,iwid,weights,strata))
colnames(modeldata)<-c("present","parent","spouse","siblings","children","parentinlaw","friend_diff","no_companion","traditions","rltp_partents","rltp_spouse","rltp_siblings",  "secret_spouse","secret_parent","hh_hit","hh_insult","event_mixed","age","gender","edu","nfamily","employ","muni", "marital","bidr", "language_iw","nationality","age_iw","edu_iw","exp_iw","iw7b","iw7b3","iw9b",
"hexcao1","hexcao2","hexcao3","hexcao4","hexcao5","hexcao6",
"ssi1","ssi2","ssi3","ssi4","ssi5","ssi6",
"iwid","weights","strata")
str(modeldata)

for(i in c(7:45,47)){
  modeldata[,i]<-as.numeric(as.character(modeldata[,i]))
}

write.csv2(modeldata,file=paste0(dir,"modeldata2.csv"),row.names =F)
colnames(modeldata)

```

##friend_diff 1
```{r friend_diff 1}
m1_1<-clm(factor(friend_diff) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m1_1)

```

##friend_diff 2
```{r friend_diff 2}
m1_2<-clmm(factor(friend_diff) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m1_2)

```


##friend_diff 3
```{r friend_diff 3}
m1_3<-clmm(factor(friend_diff) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+ factor(language_iw) +factor(nationality)+factor(edu_iw)+factor(exp_iw)
+hexcao[,2]+hexcao[,3] +hexcao[,5]
     +ssi[,1]+ssi[,2]+ssi[,5]+ssi[,6]+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m1_3)

```


##no_companion 1
```{r no_companion 1}
m2_1<-clm(factor(no_companion) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m2_1)

```

##no_companion 2
```{r no_companion 2}
m2_2<-clmm(factor(no_companion) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m2_2)

```


##no_companion 3
```{r no_companion 3}
m2_3<-clmm(factor(no_companion) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+ factor(language_iw) +factor(nationality)+factor(edu_iw)+factor(exp_iw)
+hexcao[,2]+hexcao[,3] +hexcao[,5]
     +ssi[,1]+ssi[,2]+ssi[,5]+ssi[,6]+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m2_3)
```


##traditions 1
```{r traditions 1}
m3_1<-clm(factor(traditions) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m3_1)

```

##traditions 2
```{r traditions 2}
m3_2<-clmm(factor(traditions) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m3_2)

```

##traditions 3
```{r traditions 3}
m3_3<-clmm(factor(traditions) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+ factor(language_iw) +factor(nationality)+factor(edu_iw)+factor(exp_iw)
+hexcao[,2]+hexcao[,3] +hexcao[,5]
     +ssi[,1]+ssi[,2]+ssi[,5]+ssi[,6]+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m3_3)

```


##rlp_parents 1
```{r rltp_partents 1}
m4_1<-glm(factor(rltp_partents) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),family = binomial, na.action=na.omit,weights = weights,data=modeldata)
summary(m4_1)
```

##rlp_parents 2
```{r rltp_partents 2}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$rltp_partents)==F,]
m4_2<-glmer(factor(subdata$rltp_partents) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m4_2)
```


##rlp_parents 3
```{r rltp_partents 3}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$rltp_partents)==F,]
m4_3<-glmer(factor(subdata$rltp_partents) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+factor(subdata$language_iw) +factor(subdata$nationality)+factor(subdata$edu_iw)+factor(subdata$exp_iw)
+subdata$hexcao2+subdata$hexcao3 +subdata$hexcao5
     +subdata$ssi1+subdata$ssi2+subdata$ssi5+subdata$ssi6+
              (1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m4_3)
```


##rlp_spouse 1
```{r rltp_spouse 1}
m5_1<-glm(factor(rltp_spouse) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni),family = binomial, na.action=na.omit,weights = weights,data=modeldata)
summary(m5_1)
```

##rltp_spouse 2
```{r rltp_spouse 2}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$rltp_spouse)==F,]
m5_2<-glmer(factor(subdata$rltp_spouse) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m5_2)
```

##rlp_spouse 3
```{r rltp_spouse 3}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$rltp_spouse)==F,]
m5_3<-glmer(factor(subdata$rltp_spouse) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$language_iw) +factor(subdata$nationality)+factor(subdata$edu_iw)+factor(subdata$exp_iw)
+subdata$hexcao2+subdata$hexcao3 +subdata$hexcao5
     +subdata$ssi1+subdata$ssi2+subdata$ssi5+subdata$ssi6+
              (1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m5_3)
```


##rltp_siblings 1
```{r rltp_siblings 1}
m6_1<-glm(factor(rltp_siblings) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),family = binomial, na.action=na.omit,weights = weights,data=modeldata)
summary(m6_1)
```

##rltp_siblings 2
```{r rltp_siblings 2}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$rltp_siblings)==F,]
m6_2<-glmer(factor(subdata$rltp_siblings) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m6_2)
```

##rltp_siblings 3
```{r rltp_siblings 3}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$rltp_siblings)==F,]
m6_3<-glmer(factor(subdata$rltp_siblings) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+factor(subdata$language_iw) +factor(subdata$nationality)+factor(subdata$edu_iw)+factor(subdata$exp_iw)
+subdata$hexcao2+subdata$hexcao3 +subdata$hexcao5
     +subdata$ssi1+subdata$ssi2+subdata$ssi5+subdata$ssi6+
              (1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m6_3)
```


##secret_spouse 1
```{r secret_spouse 1}
m7_1<-glm(factor(secret_spouse) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni),family = binomial, na.action=na.omit,weights = weights,data=modeldata)
summary(m7_1)
```

##secret_spouse 2
```{r secret_spouse 2}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$secret_spouse)==F,]
m7_2<-glmer(factor(subdata$secret_spouse) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m7_2)
```

##secret_spouse 3
```{r secret_spouse 3}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$secret_spouse)==F,]
m7_3<-glmer(factor(subdata$secret_spouse) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$language_iw) +factor(subdata$nationality)+factor(subdata$edu_iw)+factor(subdata$exp_iw)
+subdata$hexcao2+subdata$hexcao3 +subdata$hexcao5
     +subdata$ssi1+subdata$ssi2+subdata$ssi5+subdata$ssi6+
              (1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m7_3)
```


##secret_parents 1
```{r secret_parent 1}
m8_1<-glm(factor(secret_parent) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),family = binomial, na.action=na.omit,weights = weights,data=modeldata)
summary(m8_1)
```

##secret_parent 2
```{r secret_parent 2}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$secret_parent)==F,]
m8_2<-glmer(factor(subdata$secret_parent) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m8_2)
```

##secret_parent 3
```{r secret_parent 3}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$secret_parent)==F,]
m8_3<-glmer(factor(subdata$secret_parent) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+factor(subdata$language_iw) +factor(subdata$nationality)+factor(subdata$edu_iw)+factor(subdata$exp_iw)
+subdata$hexcao2+subdata$hexcao3 +subdata$hexcao5
     +subdata$ssi1+subdata$ssi2+subdata$ssi5+subdata$ssi6+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m8_3)
```

##hh_hit
```{r hh_hit 1}
m9_1<-glm(factor(hh_hit) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),family = binomial, na.action=na.omit,weights = weights,data=modeldata)
summary(m9_1)
```

##hh_hit 2
```{r hh_hit 2}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$hh_hit)==F,]
m9_2<-glmer(factor(subdata$hh_hit) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m9_2)
```

##hh_hit 3
```{r hh_hit 3}
#subdata<-modeldata[complete.cases(modeldata),]
subdata<-modeldata[is.na(modeldata$hh_hit)==F,]
m9_3<-glmer(factor(subdata$hh_hit) ~factor(subdata$parent)+factor(subdata$spouse)+factor(subdata$siblings)+factor(subdata$children)+factor(subdata$parentinlaw)+subdata$bidr+subdata$age+factor(subdata$gender)+factor(subdata$edu)+factor(subdata$nfamily)+factor(subdata$employ)+factor(subdata$muni)+factor(subdata$marital)+factor(subdata$language_iw) +factor(subdata$nationality)+factor(subdata$edu_iw)+factor(subdata$exp_iw)
+subdata$hexcao2+subdata$hexcao3 +subdata$hexcao5
     +subdata$ssi1+subdata$ssi2+subdata$ssi5+subdata$ssi6+(1|factor(subdata$iwid)),family = binomial("logit"),weights = subdata$weights,data=subdata,control=glmerControl(calc.derivs = F))
summary(m9_3)
```

##hh_insult 1
```{r hh_insult 1}
m10_1<-clm(factor(hh_insult) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m10_1)

```

##hh_insult 2
```{r hh_insult 2}
m10_2<-clmm(factor(hh_insult) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m10_2)

```

##hh_insult 3
```{r hh_insult 3}
m10_3<-clmm(factor(hh_insult) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+factor(language_iw) +factor(nationality)+factor(edu_iw)+factor(exp_iw)
+hexcao[,2]+hexcao[,3] +hexcao[,5]
     +ssi[,1]+ssi[,2]+ssi[,5]+ssi[,6]+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m10_3)

```


##event_mixed 1
```{r event_mixed 1}
m11_1<-clm(factor(event_mixed) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m11_1)

```

##event_mixed 2
```{r event_mixed 2}
m11_2<-clmm(factor(event_mixed) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m11_2)

```

##event_mixed 3
```{r event_mixed 3}
m11_3<-clmm(factor(event_mixed) ~parent+spouse+siblings+children+parentinlaw+bidr+age+factor(gender)+factor(edu)+factor(nfamily)+factor(employ)+factor(muni)+factor(marital)+factor(language_iw) +factor(nationality)+factor(edu_iw)+factor(exp_iw)
+hexcao[,2]+hexcao[,3] +hexcao[,5]
     +ssi[,1]+ssi[,2]+ssi[,5]+ssi[,6]+(1|factor(iwid)),Hess=T,link="logit", na.action=na.omit,  threshold = "flexible",weights = weights,data=modeldata,control =clmm.control(grtol=1e-6,innerCtrl = "noWarn",maxIter = 500,maxLineIter = 500))
summary(m11_3)

```


```{r}
anova(m1_2,m1_3)
anova(m2_2,m2_3)
anova(m3_2,m3_3)
anova(m4_2,m4_3)
anova(m5_2,m5_3)
anova(m6_2,m6_3)
anova(m7_2,m7_3)
anova(m8_2,m8_3)
anova(m9_2,m9_3)
anova(m10_2,m10_3)
anova(m11_2,m11_3)
```

